---
title: "Main Analysis"
author: "Jake Hughey"
date: "2022-08-17"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

### Load packages and data.

```{r, message = FALSE}
library('broom')
library('cowplot')
library('data.table')
library('foreach')
library('ggplot2')
library('haven')
library('huxtable')
library('kableExtra')
library('knitr')

theme_set(
  theme_bw() +
    theme(axis.text = element_text(color = 'black'),
          panel.grid.minor = element_blank(),
          legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = 'cm')))

dataDir = 'data'

dOrig = setDT(read_dta(file.path(dataDir, 'master.dta')))
treat_types = c('treat_pool', 'treat_target')
```

### Melt data.table to long format, scale outcomes by standard deviation of the control group, and rename stuff.

```{r, results = 'hide'}
outcomes = data.table(
  level = c('average_level', 'place_value_correct', 'operation_frac_correct'),
  label = c('Average level', 'Place value', 'Fractions'))

dMelt = melt(
  dOrig,
  id.vars = c('unique_id', 'treatment', 'treat_pool', 'treat_target', 'tarl_prev'),
  measure.vars = outcomes$level, variable.name = 'outcome_name',
  value.name = 'outcome_value', variable.factor = FALSE)
dMelt[, outcome_value := as.numeric(outcome_value)]

dMelt[
  , outcome_value := outcome_value / sd(outcome_value[treatment == 0], na.rm = TRUE),
  by = outcome_name]

dMelt[, outcome_name := factor(outcome_name, outcomes$level, outcomes$label)]

for (j in treat_types) {
  a = attr(dOrig[[j]], 'labels')
  dMelt[, x := factor(x, a, names(a)), env = list(x = j)]}
```

### Run linear regression on each outcome (although a couple are binary) for both codings of treatment variable, and for the "aggregated" treatment.

`lm()` automatically removes missing values.

```{r, results = 'hide'}
dFit = foreach(treat_type = treat_types, .combine = rbind) %do% {
  dMelt[
    , .(treat_type = treat_type,
        fit_sep = list(lm(outcome_value ~ x + tarl_prev, data = .SD)),
        fit_agg = list(lm(outcome_value ~ I(x != 'Control') + tarl_prev, data = .SD))),
    keyby = outcome_name, env = list(x = treat_type)]}
```

### Run an anova comparison to test equality of coefficients.

```{r, results = 'hide'}
dFit[, anova_comp := .(.(anova(fit_sep[[1L]], fit_agg[[1L]]))),
     by = .(treat_type, outcome_name)]
dFit[, p_value_comp := anova_comp[[1L]]$`Pr(>F)`[2L],
     by = .(treat_type, outcome_name)]
dFit[treat_type == 'treat_pool', p_value_comp_label := 'SMS Only = Phone + SMS']
dFit[treat_type == 'treat_target', p_value_comp_label := 'Not Targeted = Targeted']
```

### Extract model statistics from the fits.

```{r, results = 'hide'}
dTidy = dFit[
  , tidy(fit_sep[[1L]], conf.int = TRUE),
  keyby = .(treat_type, outcome_name)]

dTidy[, term := factor(
  term,
  c('(Intercept)', 'treat_poolSMS Only', 'treat_poolPhone + SMS',
    'treat_targetNot Targeted', 'treat_targetTargeted', 'tarl_prev'),
  c('Intercept', 'SMS Only', 'Phone + SMS', 'Not Targeted', 'Targeted', 'Previous TARL'))]
```

### Plot coefficients.

```{r}
p = ggplot(dTidy[!(term %in% c('Intercept', 'Previous TARL'))]) +
  geom_hline(yintercept = 0, color = 'gray', linetype = 'dashed') +
  geom_point(
    aes(x = term, y = estimate, color = outcome_name, shape = outcome_name),
    position = position_dodge(width = 0.5), size = 3) +
  geom_linerange(
    aes(x = term, ymin = conf.low, ymax = conf.high, color = outcome_name),
    position = position_dodge(width = 0.5), size = 1, alpha = 0.5) +
  labs(x = 'Treatment', y = 'Learning gains (in standard deviations)',
       color = 'Outcome', shape = 'Outcome') +
  scale_color_brewer(palette = 'Set2')
p
```

### Produce regression tables.

```{r}
fits = dFit[treat_type == 'treat_pool']$fit_sep
names(fits) = dFit[treat_type == 'treat_pool']$outcome_name

huxreg(
  fits, ci_level = 0.95,
  error_format = "({std.error})\n[{p.value}]\n{{{conf.low}, {conf.high}}}",
  coefs = c('SMS Only' = 'treat_poolSMS Only', 'Phone + SMS' = 'treat_poolPhone + SMS'),
  statistics = c('Observations' = 'nobs'))

fits = dFit[treat_type == 'treat_target']$fit_sep
names(fits) = dFit[treat_type == 'treat_target']$outcome_name

huxreg(
  fits, ci_level = 0.95,
  error_format = "({std.error})\n[{p.value}]\n{{{conf.low}, {conf.high}}}",
  coefs = c('Not Targeted' = 'treat_targetNot Targeted', 'Targeted' = 'treat_targetTargeted'),
  statistics = c('Observations' = 'nobs'))
```

### Produce table of p-values for comparing treatments.

```{r}
dComp = dcast(
  dFit, p_value_comp_label ~ outcome_name, value.var = 'p_value_comp')
setnames(dComp, 'p_value_comp_label', 'Comparison')

kable_paper(kbl(dComp, digits = 3), 'hover', full_width = FALSE)
```

### Calculate mean outcome values for the controls.

```{r}
dSummary = dMelt[
  treatment == 0,
  .(mean_control_outcome = mean(outcome_value, na.rm = TRUE)),
  keyby = outcome_name]
dSummary = dcast(
  dSummary, . ~ outcome_name, value.var = 'mean_control_outcome')[, !'.']

kable_paper(kbl(dSummary, digits = 3), 'hover', full_width = FALSE)
```
